### 2014-09-24 ms/ms.Rmd
minor glitch in acknowledgments
Kluge to avoid knitcitations bug. Closes #165

@@

Quantifying the amount of mass or energy invested in plant tissues is of fundamental interest across a range of disciplines, including ecology, forestry, ecosystem science, and climate change science `r citep(list(bib["niklas_plant_1994"],bib["chave_tree_2005"], "10.1111/j.1365-2745.2010.01735.x"))`. The allocation of net primary production into different plant components is an important process affecting the lifetime of carbon in ecosystems, and resource use and productivity by plants  `r citep(list(bib["cannell_carbon_1994"],bib["litton_carbon_2007"],bib["poorter_biomass_2012"]))`. While many scientific studies have destructively harvested woody plants, most of the data collected have only been made available in the form of summary tables or figures included in publications. Until now, the raw data has resided piecemeal on the hard drives of individual scientists spread around the world. Several studies have gathered together the fitted (allometric) equations for separate datasets `r citep(list("10.1016/S0378-1127(97)00019-4",bib["jenkins_national-scale_2003"],bib["zianis_biomass_2005"],"10.3832/ifor0901-006"))`, but none have previously attempted to organize and share the raw individual plant data underpinning these equations on a large scale. Gathered together, such data would represent an important resource for the community, meeting a widely recognized need for rich, open data resources to solve ecological problems `r citep(c("10.1016/j.tree.2013.05.002","10.1007/s13595-014-0375-3","10.1038/505160a", "10.1016/j.tree.2013.05.002"))`.

@@

Combining data from many different studies, each using its own set of terms and units, and quirks, is no trivial task `r citep(c("10.1890/1051-0761(1997)007[0330:NMFTES]2.0.CO;2","10.12688/f1000research.4518","10.1016/j.tree.2011.11.016"))`. This compilation would not have been possible without several new technologies. In particular,

@@

D.S. Falster, A. Vårhammer and D.R. Barneche were employed on an ARC discovery grant to Falster (DP110102086) and a UWS start-up grant to R.A. Duursma. R.G. FitzJohn was supported by the Science and Industry Endowment Fund (RP04-174). M.I. Ishihara was supported by the Environmental Research and Technology Development Fund (S-9-3) of the Ministry of the Environment, Japan. We thank Takahiro Inoue, Hayato Aoyama and Shin-ichiro Aiba for valuable assistance. In addition, we thank the authors thank the following people for contributions to the following studies:

>>>>

```{r precite, results='hide', message=FALSE, echo=FALSE}
# Kluge to avoid all author names being cited. Bug in knitcitations, see:
# https://github.com/cboettig/knitcitations/issues/65
citep(list(bib["niklas_plant_1994"],bib["chave_tree_2005"], "10.1111/j.1365-2745.2010.01735.x"))
citep(list(bib["cannell_carbon_1994"],bib["litton_carbon_2007"],bib["poorter_biomass_2012"]))
citep(list("10.1016/S0378-1127(97)00019-4",bib["jenkins_national-scale_2003"],bib["zianis_biomass_2005"],"10.3832/ifor0901-006"))
citep(c("10.1016/j.tree.2013.05.002","10.1007/s13595-014-0375-3","10.1038/505160a", "10.1016/j.tree.2013.05.002"))
citep(c("10.1890/1051-0761(1997)007[0330:NMFTES]2.0.CO;2","10.12688/f1000research.4518","10.1016/j.tree.2011.11.016"))
citep("10.1038/nj7461-243a")
```

@@

Quantifying the amount of mass or energy invested in plant tissues is of fundamental interest across a range of disciplines, including ecology, forestry, ecosystem science, and climate change science `r citep(list(bib["niklas_plant_1994"],bib["chave_tree_2005"], "10.1111/j.1365-2745.2010.01735.x"))`. The allocation of net primary production into different plant components is an important process affecting the lifetime of carbon in ecosystems, and resource use and productivity by plants  `r citep(list(bib["cannell_carbon_1994"],bib["litton_carbon_2007"],bib["poorter_biomass_2012"]))`. While many scientific studies have destructively harvested woody plants, most of the data collected have only been made available in the form of summary tables or figures included in publications. Until now, the raw data has resided piecemeal on the hard drives of individual scientists spread around the world. Several studies have gathered together the fitted (allometric) equations for separate datasets `r citep(list("10.1016/S0378-1127(97)00019-4",bib["jenkins_national-scale_2003"],bib["zianis_biomass_2005"],"10.3832/ifor0901-006"))`, but none have previously attempted to organize and share the raw individual plant data underpinning these equations on a large scale. Gathered together, such data would represent an important resource for the community, meeting a widely recognized need for rich, open data resources to solve ecological problems `r citep(c("10.1016/j.tree.2013.05.002","10.1007/s13595-014-0375-3","10.1038/505160a"))`.

@@

Combining data from many different studies, each using its own set of terms and units, and quirks, is no trivial task `r citep(c("10.1890/1051-0761(1997)007[0330:NMFTES]2.0.CO;2","10.1016/j.tree.2011.11.016","10.12688/f1000research.4518"))`. This compilation would not have been possible without several new technologies. In particular,

@@

D.S. Falster, A. Vårhammer and D.R. Barneche were employed on an ARC discovery grant to Falster (DP110102086) and a UWS start-up grant to R.A. Duursma. R.G. FitzJohn was supported by the Science and Industry Endowment Fund (RP04-174). M.I. Ishihara was supported by the Environmental Research and Technology Development Fund (S-9-3) of the Ministry of the Environment, Japan. We thank Takahiro Inoue, Hayato Aoyama and Shin-ichiro Aiba for valuable assistance. In addition, the authors thank the following people for contributions to the following studies:
